### 2017-06-05 paper/documents/2.background.tex
- update paper

Player roles or play styles is the way how player will choose and try to act as their roles or styles in the games. It is important to note that these roles describe a different facet of play than classic player type classifications (e.g. after battle

>>>>

Player roles or play styles is the way how player will choose and try to act as their roles or styles in the games. It is important to note that these roles describe a different facet of play than classic player type classifications (e.g. after Bartle \cite{bartle1996hearts}) which aim to classify expressed character traits of the players and were designed to match role-play style games. Comparison of videos, Online guides, and commentary of professional players and commentators are our sources for selection and characterization of the player roles. Player roles definitions and naming conventions will in any case differ slightly among the player base and shift over time as the game evolves, constituting another challenge for \textit{Machine Learning} applications in this area. We isolated five player roles for the main \textit{Machine Learning} task, which strike a balance between covering common play styles in great detail while leaving out some exotic styles which are rarely observed or are minor variations of the other styles. The isolated roles were: \textit{Carry} - who are usually weak and need protection early on, but are very strong in later stages, often deciding games. Carry typically end up with a high amount of last hits, gold per minute and overall kills, but they can get them in quite different ways.
